---
title: "Course Summary"
author: "Matt"
date: "October 21, 2016"
output: html_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
## Day 1: Packages and Version Control

We learned to create a package using [devtools][1]. The way to get started is to create the skeleton of a package
```
library(devtools)
create("Elbo")
```
This creates a directory with a couple files and a folder.
We then did the following:

1. The DESCRIPTION contains info about the package; we edited it for our purposes.
2. We looked at the NAMESPACE, but didn't modify it.
3. We created our first function in the R folder, `hi()`.

We then used [roxygen2][] to add documentation to the function,

manage source code using [github][].

```{r simple-example}
1+1
```

```{python hello}
print('hello')
```

```{r elbohi}
setwd("/home/mattnlana/Desktop")
devtools::install("Elbo")
library(Elbo)
hi("Martin")
```

[1]:https://cran.r-project.org/package=devtools
[roxygen2]://cran.r-project.org/package=roxygen2
[github]://